Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-03 src/paper.tex
update

\title{Exploration in Target Speaker Extraction using Discrete Representations and Language Models
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\section{Introduction}
Speech separation, the so-called cocktail party problem \cite{cocktail}, focuses on separating each individual speaker's source from a mixture with multiple speakers. This task is easy for humans but not for computers. 
In real life, speech signals are usually companied with background noise or other speakers' speeches. 
These corrupted signals may not be optimal for tasks like speaker verification \cite{rao2019targetspeakerextractionoverlapped,9414017}, and speech recognition \cite{molkov2017SpeakerAwareNN, 8462661}, emphasizing the importance of this task.

@@

Recently, self-supervised Learning (SSL) models like HuBERT \cite{hubert} and WavLM \cite{wavlm} have demonstrated
excellent performances on many downstream tasks \cite{superb}. These SSL models extract  
continuous representations containing rich semantic and timbre information of a given speech.

>>>>

\title{Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\section{Introduction}
Speech separation, the so-called cocktail party problem \cite{cocktail}, focuses on separating each individual speaker's source from a mixture with multiple speakers. This task is easy for humans but not for computers. 
In real life, speech signals are usually companied with background noise or other speakers' speeches. 
These corrupted signals may not be optimal for tasks like speaker verification \cite{rao2019targetspeakerextractionoverlapped,9414017}, and speech recognition \cite{molkov2017SpeakerAwareNN, 8462661}, emphasizing the importance of having good and robust 
speech separation models.

@@

Discretization of audio has been studied due to the advancement of language models (LM). 
This approach translates the audio into discrete tokens simulating text vocabularies and uses LMs to 
model them. This approach simplifies audio generation tasks by transforming the complex 
regression problems into classification problems \cite{dasb}. There are currently two approaches for
audio discretization, the first one uses neural audio codecs \cite{dac}. This approach 
typically captures the acoustic features of the audio \cite{speech_tokenizer}. The second approach 
utilizes  self-supervised Learning (SSL) models like HuBERT \cite{hubert} and WavLM \cite{wavlm}.
SSL models have demonstrated 
excellent performances on many downstream tasks \cite{superb}. These SSL models extract  
continuous representations containing rich semantic and timbre information of a given speech. 
In this paper, we mainly explore how far we can go
